Online Multiclass Linear Classification with Bandit Feedback

### 2019-01-14 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
kernelized algorithm (without guarantees yet)

>>>>

Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
can be extended to nonlinear classification using kernels~\cite{Scholkopf-Smola-Bach-2002}.
For each class, as opposed
to explicitly maintaining the weights for each class, we maintain
the set of examples whose scaled feature transformations are added to the weights.
We give a formal description in Algorithm~\ref{algorithm:kernelized}.

\begin{algorithm}[h]
\caption{\textsc{Kernelized Bandit Algorithm}
\label{algorithm:kernelized}}
\begin{algorithmic}[1]
{
\REQUIRE{Number of classes $K$.}
\REQUIRE{Number of rounds $T$.}
\REQUIRE{Kernel function  $k(\cdot, \cdot)$.}
\STATE{Initialize $J_1^{(1)} = J_2^{(1)} = \dots = J_K^{(1)} = \emptyset$}
\FOR{$t=1,2,\dots,T$}
\STATE{Observe feature vector $x_t$.}
\STATE{Compute $S_t = \left\{ i ~:~ 1 \le i \le K, \ \sum_{(x,y) \in J_i^{(t)}} y k(x, x_t) \ge 0 \right\}$}
\IF{$S_t = \emptyset$}
\STATE{Predict $\widehat y_t \sim \text{Uniform}(\{1,2,\dots,K\})$}
\STATE{Observe feedback $z_t \in \{0,1\}$ \\ \qquad where $z_t = \indicator{\widehat y_t \neq y_t}$}
\IF{$z_t = 1$}
\STATE{Set $J_i^{(t+1)} = J_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
\ELSE
\STATE{Set $J_i^{(t+1)} = J_i^{(t)}$ \\ \qquad  for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
\STATE{Update $J_{\widehat y_t}^{(t+1)} = J_{\widehat y_t}^{(t)} \cup \cbr{(x_t, +1)}$}
\ENDIF
\ELSE
\STATE{Predict $\widehat y_t \in S_t$ chosen arbitrarily}
\STATE{Observe feedback $z_t \in \{0,1\}$ \\ \qquad where $z_t = \indicator{\widehat y_t \neq y_t}$}
\IF{$z_t = 1$}
\STATE{Set $J_i^{(t+1)} = J_i^{(t)}$ \\ \qquad for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
\STATE{Update $J_{\widehat y_t}^{(t+1)} = J_{\widehat y_t}^{(t)} \cup \cbr{(x_t, -1)}$}
\ELSE
\STATE{Set $J_i^{(t+1)} = J_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
\ENDIF
\ENDIF
\ENDFOR
}
\end{algorithmic}
\end{algorithm}

### 2019-01-14 ICML-submission/introduction.tex
Add margin theorem
kernelized algorithm (without guarantees yet)

We study the problem of \textsc{Online Multiclass Linear Classification with
Bandit Feedback}~\citep{Kakade-Shalev-Shwartz-Tewari-2008}. The problem can be
viewed as a repeated game between the learner and the adversary. At each timestep $t$,
the adversary chooses a labeled example $(x_t, y_t)$ where the feature vector, $x_t \in
\R^d$ is revealed to the learner and the correct label $y_t$ is kept secret by
the adversary. Upon receiving the feature vector $x_t$, the learner is asked to
make a prediction $\widehat{y}_t$. Immediately after making its prediction, the
learner receives a feedback. In contrast with the standard full information
setting (where the feedback given is the correct label $y_t$), here the feedback
is only a binary indicator of whether the prediction was correct or not. The
protocol of the problem is formally stated below.

\begin{algorithm}[h]
\caption{\textsc{Online Multiclass Classification with Bandit Feedback}
\label{algorithm:game-protocol}}
\begin{algorithmic}[1]
{
\REQUIRE{Number of classes $K$.}
\REQUIRE{Number of rounds $T$.}
\FOR{$t=1,2,\dots,T$}
\STATE{Observe feature vector $x_t$}
\STATE{Adversary \emph{secretly} chooses correct class label $y_t \in \{1,2,\dots,K\}$}
\chicheng{Or we simply say: Adversary chooses example $(x_t, y_t)$, where $x_t$ is reveal to the learner.}
\STATE{Predict class label $\widehat y_t \in \{1,2,\dots,K\}$}
\STATE{Observe feedback $z_t \in \{0,1\}$ \\ \qquad where $z_t = \begin{cases}
0 & \text{if $\widehat y_t = y_t$,} \\
1 & \text{if $\widehat y_t \neq y_t$.}
\end{cases}$
}
\ENDFOR
}
\end{algorithmic}
\end{algorithm}

>>>>

We study the problem of \textsc{Online Multiclass Linear Classification with
Bandit Feedback}~\citep{Kakade-Shalev-Shwartz-Tewari-2008}. The problem can be
viewed as a repeated game between the learner and the adversary. At each timestep $t$,
the adversary chooses a labeled example $(x_t, y_t)$ where the feature vector $x_t \in
\R^d$ is revealed to the learner and the correct label $y_t$ is kept secret by
the adversary. Upon receiving the feature vector $x_t$, the learner is asked to
make a prediction $\widehat{y}_t$. Immediately after making its prediction, the
learner receives a feedback. In contrast with the standard full information
setting (where the feedback given is the correct label $y_t$), here the feedback
is only a binary indicator of whether the prediction was correct or not. The
protocol of the problem is formally stated below.

\begin{protocol}[h]
\caption{\textsc{Online Multiclass Classification with Bandit Feedback}
\label{algorithm:game-protocol}}
\begin{algorithmic}[1]
{
\REQUIRE{Number of classes $K$, number of rounds $T$.}
%\REQUIRE{.}
\FOR{$t=1,2,\dots,T$}
\STATE Adversary chooses example $(x_t, y_t)$, where $x_t$ is revealed to the learner.
%\STATE{Observe feature vector $x_t$}
%\STATE{Adversary \emph{secretly} chooses correct class label $y_t \in \{1,2,\dots,K\}$}
%\chicheng{Or we simply say: Adversary chooses example $(x_t, y_t)$, where $x_t$ is revealed to the learner.}
\STATE{Predict class label $\widehat y_t \in \{1,2,\dots,K\}$}
\STATE{Observe feedback $z_t \in \{0,1\}$ \\ \qquad where $z_t = \begin{cases}
0 & \text{if $\widehat y_t = y_t$,} \\
1 & \text{if $\widehat y_t \neq y_t$.}
\end{cases}$
}
\ENDFOR
}
\end{algorithmic}
\end{protocol}
